---
title: "The fans stay loyal, the players move on"
author: "Uwe Sterr"
date: "July 2016"
output:
  html_document:
    code_folding: hide
    collapsed: no
    css: style.css
    highlight: tango
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    code_folding: hide
    collapsed: no
    css: style.css
    highlight: tango
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r, message=FALSE, warning=FALSE, comment=NA, functions, fig.width=10, results="asis", tidy=F}

library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(broom)
library(magrittr)
library(plotly)
library(RSQLite)
library(reshape2)
library(visNetwork)
library(networkD3)
library(jsonlite)
library(RColorBrewer)
library(gplots)
library(knitr)
library(DT)
library(data.table)
library(d3heatmap)
library(viridis)
library(maps)
library(ggmap)
library(circlize)

rm(list = ls())
Saison <-2012

# Functions ---------------------------------------------------------------


rsplit <- function(x) {
  x <- x[!is.na(x[,1]),,drop=FALSE]
  if(nrow(x)==0) return(NULL)
  if(ncol(x)==1) return(lapply(x[,1], function(v) list(name=v)))
  s <- split(x[,-1, drop=FALSE], x[,1])
  unname(mapply(function(v,n) {if(!is.null(v)) list(name=n, children=v) else list(name=n)}, lapply(s, rsplit), names(s), SIMPLIFY=FALSE))
}


# Connect to data base ----------------------------------------------------
con <- dbConnect(SQLite(), dbname="input/database.sqlite")
# con <- dbConnect(SQLite(), dbname="database160721.sqlite")
# list all tables
# dbListTables(con)

player       <- tbl_df(dbGetQuery(con,"SELECT * FROM player"))
# player_stats <- tbl_df(dbGetQuery(con,"SELECT * FROM player_stats"))
Match        <- tbl_df(dbGetQuery(con,"SELECT * FROM Match"))
Team        <- tbl_df(dbGetQuery(con,"SELECT * FROM Team"))
Country        <- tbl_df(dbGetQuery(con,"SELECT * FROM Country"))
League        <- tbl_df(dbGetQuery(con,"SELECT * FROM League"))

```

## Find connections between different tables
```{r, message=FALSE, warning=FALSE, comment=NA, fig.width=10, results="asis", tidy=F}

library(visNetwork)
  # this function creates a data.frame with the name of the data.frame and the names of the columns of that data.frame
  create_df_of_names = function(df, name){
    data.frame(from = name, to = names(df))
  }
      list_of_df <- list(player = player,Match = Match, Team = Team, Country = Country, League = League) 

  create_vis_network <- function(list_of_df) {
    # create a names list of the data.frames
    # and map them to build one data.frame with two columns
    # - from contains all  data.frame names
    # - to  contains all column names
    edge <- map2_df(list_of_df,names(list_of_df), create_df_of_names)
    
    # create a visNetwork
    
    nodesFrom <-  edge %>% cbind(unlist(.$from),"Table") %>% select(3,4) %>% data.frame  
    nodesTo <-  edge %>% cbind(unlist(.$to),"Attribute") %>% select(3,4) %>% data.frame 
    
    names(nodesFrom) <- c("id", "group")
    names(nodesTo) <- c("id", "group")
    
    nodes <- rbind(nodesFrom,nodesTo) %>% unique() 
    nodes$id <- as.character((nodes$id))  
    nodes <- nodes %>% unique() %>% arrange(id)
    visNetwork(nodes, edge)%>%
      visOptions(highlightNearest = list(enabled = TRUE, degree = 2), nodesIdSelection = TRUE) %>%
      visEdges(arrows = "to") %>%  
      visGroups(groupname = "Table",     shape = "icon", icon = list(code = "f114", color = "green",size = 75)) %>%
      visGroups(groupname = "Attribute", shape = "icon", icon = list(code = "f115", color = "lightgreen", size = 45)) %>%
      addFontAwesome() 
    # list of icons http://astronautweb.co/snippet/font-awesome/
  }
  
  create_vis_network(list_of_df)

```


## Select relevant columns

```{r}

player  <- select(player,player_api_id, player_name) # use player_api_id as key for join
Team    <- select(Team, team_api_id, team_long_name, team_short_name) # use team_api_id as key for join
Country <-select(Country, id, name) %>% rename(country_id = id)  %>% rename(country_name = name)   # use country_id as key for join
League  <- select(League, country_id, name) %>% rename(league_name = name) # use country_id as key for join
Match   <-select(Match, id, country_id, league_id, season, stage, date, match_api_id, home_team_api_id, away_team_api_id, home_team_goal, away_team_goal, home_player_1, home_player_2, home_player_3, home_player_4, home_player_5, home_player_6, home_player_7, home_player_8, home_player_9, home_player_10, home_player_11, away_player_1, away_player_2, away_player_3, away_player_4, away_player_5, away_player_6, away_player_7, away_player_8, away_player_9, away_player_10, away_player_11, goal, shoton, shotoff, foulcommit, card, cross, corner, possession)


```

## Join the tables so that all information is available from matchMelt

```{r}
# melt match data to generate df with player names in one column ----------
matchMelt <-melt(Match,id = c(1:11), measure=c(12:33),na.rm = TRUE, value.name = "player_api_id") %>% 
  mutate(team_api_id=ifelse(grepl("home",variable),home_team_api_id,
                            ifelse(grepl("away",variable),away_team_api_id,NA))) %>%  # get longer names by joining appropriate data.frames
  left_join(Team, by = "team_api_id") %>%
  left_join(player, by = "player_api_id") %>% # add club to each player
  left_join(Country, by = "country_id") %>% # add club to each player
  left_join(League, by = "country_id") %>% # add club to each player
  separate(season, into=c("saisonStart","saisonEnd"),sep = "/", convert = TRUE)  # split saison so it integer
      list_of_df <- list(player = player,matchMelt = matchMelt, Team = Team, Country = Country, League = League) 
  create_vis_network(list_of_df)
```



## Built league table in format data.table because the composite key was easier to create with data.table keycols = c("season", "league_id", "home_team_api_id" )


```{r}



PointsDf <-Match %>% 
  select(1:11)  %>% 
  mutate(homePoint = if_else((home_team_goal > away_team_goal),3,if_else((home_team_goal == away_team_goal),1,0))) %>%
  mutate(awayPoint = if_else((home_team_goal > away_team_goal),0,if_else((home_team_goal == away_team_goal),1,3))) 

# Create home and way tables which will be combined to calculate total points

tableHomeDt <- PointsDf %>% 
  group_by(season, league_id, home_team_api_id) %>%
  summarise(pointsHome = sum(homePoint)) %>%
  ungroup() %>% data.table
  
  keycols = c("season", "league_id", "home_team_api_id" )
setkeyv(tableHomeDt,keycols) 

tableAwayDt <- PointsDf %>% 
  group_by(season, league_id, away_team_api_id) %>%
  summarise(pointsAway = sum(awayPoint)) %>%
  ungroup()  %>% data.table 
  keycols = c("season", "league_id", "away_team_api_id" )
setkeyv(tableAwayDt,keycols) 

# combine the two tables and create ranking
tableHomeAwayDt <- tableHomeDt[tableAwayDt, nomatch=0] %>%
  mutate(points = pointsHome + pointsAway) %>%
  group_by(season, league_id)  %>%
  mutate(rank = min_rank(desc(points)))

tableLong <- tableHomeAwayDt %>% 
  left_join(League, by = c("league_id" = "country_id")) %>%
  left_join(Team, by = c("home_team_api_id" = "team_api_id")) %>%
  ungroup() %>%
  select(season, league_name, rank, team_long_name, points)



```

## Create Transfer data.frame

```{r}

TransferDf <-matchMelt %>%
  select(player_name, team_long_name, team_short_name, saisonStart, saisonEnd, country_name, league_name)  %>%
  group_by(player_name,team_long_name) %>% # now we have all players with their team
  arrange(saisonStart)  %>% 
  summarise(Player = first(player_name), ClubFirst = min(saisonStart),ClubLast = max(saisonEnd), Country = first(country_name), League = first(league_name)) %>%
# now players first and last game for a club is found
  arrange(ClubFirst) %>%
  mutate(FormerClub = lag(team_long_name)) %>%
  mutate(CurrentClub = team_long_name) %>%
  mutate(FormerLeague = lag(League)) %>%
  mutate(CurrentLeague = League) %>%
  mutate(FormerCountry = lag(Country)) %>%
  mutate(CurrentCountry = Country) %>%
  select(Player, CurrentClub,	FormerClub,	ClubFirst,	ClubLast, CurrentLeague, FormerLeague, CurrentCountry, FormerCountry)




```

## Define function for VisNetwork used later

```{r}

visNetworkPerClub  <- function(matchMelt, Club, Saison)
{
PlayerSelected <- matchMelt  %>%
  filter(saisonStart == Saison) %>% 
  filter(team_long_name == Club) %>%
  select(player_name) %>%
  unique()


edges <- matchMelt %>%
  filter(saisonStart>= Saison) %>%
  filter(player_name %in% PlayerSelected$player_name)  %>%
  select(c(team_long_name,player_name)) %>%
  rename(from = team_long_name)  %>%
  rename(to = player_name) %>%
  unique()  %>% 
  mutate(arrows = c("from"))

edgesMelt <- edges %>%
  mutate(shape = "") %>%
  melt(id = "shape", measure = c("to", "from"), value.name = "id")

nodesClub <- edgesMelt %>%
  filter(variable == "from") %>%
  mutate(group = c("Club"))

nodesPlayer <- edgesMelt %>%
  filter(variable == "to") %>%
  mutate(group = c("Player")) 

nodes <- rbind(nodesClub,nodesPlayer) %>% select(c(variable,id, group)) %>% unique()  

visNetwork(nodes, edges, main = list(text = paste0("Where did the player of ", Club, " play after 2012" ),
 style = "font-family:Comic Sans MS;color:#ff0000;font-size:15px;text-align:center;")) %>%
  visGroups( groupname = "Player", color = "lightgreen") %>%
  visGroups( groupname = "Club", color = "lightblue") %>%
  visOptions(highlightNearest = list(enabled = TRUE, degree =1), nodesIdSelection = FALSE) %>%
  visInteraction(dragNodes = FALSE, dragView = FALSE, zoomView = FALSE)  %>%
  visGroups(groupname = "Club", shape = "icon", icon = list(code = "f1e3", size = 75)) %>%
  visGroups(groupname = "Player", shape = "icon", icon = list(code = "f183", color = "green")) %>%
  addFontAwesome() %>%
  visInteraction(navigationButtons = TRUE) 
}

# Set variable for VisNetwork, when to look at where players go afterwards


```

***  

# The fans stay loyal and the players move on!


Don't know how you feel, but when I see the players kiss their shirt and then move on to the next club I feel a little bit deluded.  
In the following graphs the move of players through the leagues and between the clubs are shown.  
  
- Lets see how the leagues compare
- How are the big teams compare?
- How did their points evolve over time?
- See who is cashing in by changing the clubs many times

The analysis is based on a kaggle dataset  https://www.kaggle.com/hugomathien/soccer

First let us look at the transfers since 2008 in a chord digram. Please note that an D3 based interactive version of chord diagrams is available in the package "chorddiag", however, this package is not available on Kaggle. Check code to see how to integrate the interactive version.
  
The chord diagram links the two leagues with an arc, the end of the arc scales with the number of players transferd from that country to the country on the other end of the arc. E.g. see the arc from Portugal to Spain. On the Portugal side the arc is wider than on the Spain side because more players move from Portugal to Spain than vica versa. And since the total number of transfers of the two countries is similar the width of the arc can be compared directly.


***


<h2 align="center">Chord diagram of transfers between leagues</h2>

```{r , Chorddiag, fig.height=10, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}

TransferMatrix <- na.omit(TransferDf)  %>% ungroup() %>% group_by(FormerLeague, CurrentLeague) %>%
 summarise(sub = n()) %>% ungroup() %>%  na.omit()  %>%
   mutate_each(funs(factor), FormerLeague:CurrentLeague) %>% acast(FormerLeague ~ CurrentLeague, value.var = "sub") # now matrix with leagues on both dimensions

kaggle <- 0


if (kaggle == 0) {
   library(chorddiag)
chorddiag(TransferMatrix)
} else {
   chordDiagram(TransferMatrix)
circos.clear()
}
```

***
Lets see how the numbers look like. Italy has almost twice as much transfers as Germany, with the new TV money floating around in England I guess soon there will be an inrease in transfers to England.

<h2 align="center">Number of transfers between leagues in table format</h2>

```{r}
na.omit(TransferDf)  %>% ungroup() %>% group_by(FormerLeague) %>%
 summarise(NumberOfTransfers = n()) %>% arrange(desc(NumberOfTransfers))  %>% 
  datatable( rownames = FALSE, colnames =c("League", "Number of transfers since 2008") ,options = list(dom = 't', autoWidth = TRUE, columnDefs = list(list(width = '250px', targets = c(1)))))
```

  
    
     
Italy has the highest volume on transfers, the bulk of it within the league. Surprisingly the Scottish league has the lowest number of transfers.

***
  
<br><br>
<h2 align="center">Number of transfers within leagues in table format</h2>

```{r}
# note "filter_" expects as second argument a logical predicates becuase this time we don't test content of column but if two column have equal content.
na.omit(TransferDf)  %>% ungroup() %>% filter_("FormerLeague==CurrentLeague") %>% group_by(FormerLeague) %>% summarise(NumberOfTransfers = n()) %>% arrange(desc(NumberOfTransfers))  %>% 
  
  datatable( rownames = FALSE, colnames =c("League", "Number of transfers within league since 2008") ,options = list(dom = 't', autoWidth = TRUE,
  columnDefs = list(list(width = '250px', targets = c(1)))))
```

<br><br>

Other than Spain and Portugal swapping place the same pattern is seen in the in-league transfers.

***  

<br><br>


## Where did players of the season  `r Saison` play since then?  {.tabset .tabset-fade .tabset-pills}

**Zoom and select nodes to get more insight, navigate with the tabs to the club your are most interested in.**  
The arrowhead indicates that the player played for that team

1. Top tabs let you choose the league
1. Second row tabs let you choose teams within the selected league

+ Check out Rafael from ManU, he played for 5 teams.
+ Guess how many players went from playing for Real to SSC Napoli?  
  
  

### English league

*** 

####  {.tabset .tabset-fade .tabset-pills}


##### ManU
***
```{r , VisNetworkManu, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Manchester United"
visNetworkPerClub(matchMelt, Club, Saison)

```



##### Arsenal
***
```{r , VisNetworkArsenal, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Arsenal"
visNetworkPerClub(matchMelt, Club, Saison)
```

### German league

***

#### {.tabset .tabset-fade .tabset-pills}

##### Bayern
***
```{r , VisNetworkBayern, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Bayern Munich"
visNetworkPerClub(matchMelt, Club, Saison)
```

##### Dortmund
***

```{r , VisNetworkDort, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Borussia Dortmund"
visNetworkPerClub(matchMelt, Club, Saison)
```


##### VFB Stuttgart 
***

```{r , VisNetworkStuggi, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "VfB Stuttgart"
visNetworkPerClub(matchMelt, Club, Saison)
```



### Spanish league

***

#### {.tabset .tabset-fade .tabset-pills}

##### Real
***
```{r , VisNetworkReal, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Real Madrid"
visNetworkPerClub(matchMelt, Club, Saison)
```

##### Barca
***

```{r , VisNetworkBarca, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Barcelona"
visNetworkPerClub(matchMelt, Club, Saison)
```

That was intersting, but how much are certain clubs tied together over the years?

***  
<br><br>

## Club links with more than 3 transferes between clubs since `r Saison`
**Hover over edges to find the number of transfers betweeen the clubs, hover over the nodes to see the league of the club**

**Incredible**, 10 players went from Fiorentina to Hannover, god, Hannover must be wonderful to life in compared to Florence...
  
- Check out your favorit team by using the **select list input control**
- Zoom in to make labels readable
- Click on nodes to see how the are connected
***
  

<h2 align="center">Network of club transfers, zoom in for details</h2>
```{r , ClubTransfere, fig.width= 11, fig.height=8,  warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}

# filter values
transfereSince <- 2012
minTransfers <- 3

edges <-matchMelt %>%
  select(player_name, team_long_name, saisonStart, saisonEnd, country_id, league_name)  %>%
  group_by(player_name,team_long_name) %>%
  summarise(Player = first(player_name), FirstForClub = min(saisonStart),LastForClub = max(saisonEnd), Country = first(country_id), League = first(league_name)) %>%
  filter(LastForClub >= transfereSince) %>%
  mutate(OldClub = lag(team_long_name))  %>%
  mutate(CountryFrom = lag(Country))   %>%  # not correct
  mutate(CountryTo = Country) %>%
  na.omit() %>%
  rename(to = team_long_name)  %>%
  rename(from = OldClub) %>%
  summarise(value = n_distinct(c(from,to)),to = first(to), from = first(from) , colorTo = first(CountryTo),
            colorFrom = last(CountryFrom), League = first(League))  %>%
  select(to, from, value, colorTo, colorFrom, League) %>%
  filter(value > minTransfers)  %>%
  mutate( title = paste("#Trans = ", value, " since: ", transfereSince)) %>%
  unique() 


nodes <- data.frame(c(edges$to,edges$from)) %>% unique() # create node dataframe
names(nodes)[1]<-"idNode"
 # add league id to nodes to determine color of nodes according to league

nodes <- inner_join(nodes, matchMelt, c("idNode" = "team_long_name")) %>%
  select(idNode, league_name) %>% unique() %>% rename(title = league_name)
# add color accoring to league
League <- League %>% mutate(color = mypalette<-brewer.pal(11,"Paired"))
nodes <- left_join(nodes, League, c("title" = "league_name")) %>% rename(id = idNode)
nodes <- select(nodes, id, color, title)  %>% arrange(id)

#  https://cran.r-project.org/web/packages/visNetwork/vignettes/Introduction-to-visNetwork.html  


visNetwork(nodes, edges) %>%
  visGroups( groupname = "OldClub", color = "lightgreen") %>%
  visOptions(highlightNearest = list(enabled = TRUE, degree =1), nodesIdSelection = TRUE) %>%
  visEdges(arrows = "to") %>%
  visInteraction(dragNodes = FALSE, dragView = FALSE, zoomView = FALSE)  %>%
  visLegend() %>%
  visInteraction(navigationButtons = TRUE)  %>%
  visPhysics(stabilization = TRUE, maxVelocity = 10) 
```

***  

<br><br>

## How did it work out for the teams, all tables of all leagues since 2008/2009

Just type in search field **"england 2008/2009"** to get premiere league table of season 2008/2009, or **"bundes 2011/2012"** for German Bundesliga of season 2011/2012 and sort for "Rank". BTW, the table considers **only points**, not goal difference, gives at times a better feeling about how close the whole thing often is, especially at the bottom of the table.

***
<h3 align="center">Interactive table to show league tables of selected leagues and season</h3>
```{r , League1, fig.width=15 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
datatable(tableLong, rownames = FALSE, colnames =c("Season", "League", "Rank", "Team", "Points"),options = list(
  order = list(list(2, 'asc')), pageLength = 25, search = list(search = 'england 2015/2016')))

```

***  

<br><br>

## Heatmaps of Clubs in Leagues, how many points did they have at the end of the season
Points express better than ranking the strength of a team. After all, ranking is relative, one season the team can be champion with 80 points, next season its only worth 3rd place.


```{r, fig.height = 10, fig.width = 10}

tableLong$points <- as.factor(tableLong$points)
p <- ggplot(filter(tableLong, league_name %in% c("Germany 1. Bundesliga", "England Premier League" )), mapping = aes(x = season, y = team_long_name)) + 
  geom_tile(mapping = aes(fill = points),color="white", size=0.1 ) + facet_grid(league_name~., scales = "free_y") +scale_fill_viridis(discrete=TRUE) + theme(legend.position = "none")  # free y scale to avoid that all clubs are on Y axis in all leagues
ggplotly(p)
```




```{r , ClubTransfereRadial, fig.width= 10, fig.height=10,  warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}

TransferRadialCLubs <- function(TransferDf, Club, Saison)
{
TransferRadialLeagues  <- TransferDf %>%
    filter(grepl(Club , FormerClub )) %>%
  filter(ClubFirst >= Saison) %>%
    as.list() %>% as.data.frame(stringsAsFactors = FALSE) %>%
   select(FormerClub, CurrentCountry, CurrentClub, Player) %>%
  arrange(FormerClub, CurrentCountry, CurrentClub, Player) 

TransferRadialList <- rsplit(TransferRadialLeagues)[[1]]
radialNetwork(TransferRadialList, fontSize = 20, height = 700, width = 1000, linkColour = "green", nodeColour = "green", nodeStroke = "lightgreen", textColour = "blue" )  
}
```

***  

<br><br>

# Where did players play since  `r Saison` , this time in a radial network just for fun


## ManU  

***  

```{r , VisNetworkRadialManu,fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Manchester United"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***

## Arsenal  

```{r , VisNetworkRadialArsenal, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Arsenal"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***
## Bayern  

```{r , VisNetworkRadialBayern, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Bayern Munich"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***
## Dortmund  


```{r , VisNetworkRadialDort, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Borussia Dortmund"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***

## VFB Stuttgart   


```{r , VisNetworkRadialStuggi, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "VfB Stuttgart"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***

## Real  

```{r , VisNetworkRadialReal, fig.width=10 ,warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}
Club <- "Real Madrid"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***
## Barca  


```{r, echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE, comment=NA, results="asis", tidy=F, VisNetworkRadialBarca}
Club <- "Barcelona"
TransferRadialCLubs(TransferDf, Club, Saison)
```

***

<br><br>

# Check Transfer dataframe with some players
Always good to check if the data is generated correctly.  
Note, the transfers were determined by the date the player played for the club, therefore there is a slight discrepancy.

**Lewandowski**  
2006–2008	Znicz Pruszków   
2008–2010	Lech Poznań  
2010–2014	Borussia Dortmund	  
2014–	Bayern Munich

**Rene Adler**  
2006–2012	Bayer Leverkusen    
2012–	Hamburger SV  

```{r , CheckTransferDf, warning=FALSE, message=FALSE,comment = NA, results = "asis", comment = NA, tidy = F}

# check with Lewandowski


 TransferDf %>% filter(grepl("Robert Lewandowski" ,Player )) %>% select(-Player)  %>% kable()

 TransferDf %>% filter(grepl("Adler" ,Player ))  %>% select(-Player)  %>% kable()

 
```

# Infos

1. datatable format https://rstudio.github.io/DT/options.html
1. map with clubs and links https://cran.r-project.org/web/packages/rworldmap/vignettes/rworldmap.pdf
2. Heatmap plot by value using ggmap  http://stackoverflow.com/questions/32148564/heatmap-plot-by-value-using-ggmap
3. Drawing Arcs on Maps 
 3.1 with theory http://dsgeek.com/2013/06/08/DrawingArcsonMaps.html
 3.2 ready to use http://flowingdata.com/2011/05/11/how-to-map-connections-with-great-circles/
4. chord diagram https://github.com/mattflor/chorddiag, doesnt run on kaggle server
5. use circlize instead 

# to does

1. create gif animation of radials to show in markdown doc




