---
title: "Gapminder for VHS 1/2017"
author: "Uwe Sterr"
date: "April 2017"
always_allow_html: yes # to allow creation of github doc with HTML elements
output:
  github_document:
    toc: yes
  html_document:
    collapsed: no
    css: style.css
    highlight: tango
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    collapsed: no
    css: style.css
    highlight: tango
    theme: readable
    toc: yes
    toc_depth: 4
    toc_float: yes
---

# Finding AIDS impact in r square

Finding information in data using statistical characteristics 
**R-squared** is a statistical measure of how close the data are to the fitted regression line

**Inspired by **

- TED talk of  **Hans Rosling**: Let my dataset change your mindset
https://www.ted.com/talks/hans_rosling_at_state#t-1176407

- **Hadley Wickham** Managing many models with R https://www.youtube.com/watch?v=rz3_FDVt9eg 




```{r}
knitr::opts_chunk$set(cache=TRUE) # renders only changes => faster
library(gapminder)
library(tidyverse)
tidyverse_packages()
```


## Peek into data

 
```{r}
summary(gapminder)
gapminder %>% filter(gdpPercap < 300)


```

### Plot data

```{r}
# Print xy plot -----------------------------------------------------------
gapminder <- gapminder %>% mutate(year1950 = year -1950)
ggplot(gapminder, aes(x=year, y=lifeExp)) +geom_line(aes(group = country))
```

### Data wrangling
lets transform the data so that we keep all of a country's data in one row

- build nested data.frame
- access elements of nested data.frame

```{r}

# Nested data -------------------------------------------------------------

by_country <- gapminder  %>%
  group_by(continent, country) %>%
  nest()

by_country                  # show content of df
str(by_country[1:3,])       # show structure of first 3 rows of grouped and nested df
by_country$data[[1]]        # show data of first row
by_country$data[1]          # show data of first row
by_country$data[[1]][[2]]   # show  contents of second column 
by_country$data[[1]][2]     # show second column
```


- [ returns a list
- [[ returns content of list

a good explanation can be found at: http://r4ds.had.co.nz/vectors.html#lists 

### Structure of dataframe

The column **data** is a list of data frames. Therefore, we have now a row per country and all data of that country in a dataframe in **one** column.

In a grouped dataframe **each row is an oberservation**, in a nested dataframe **each row is a group**, in this case, a group of a country’s observations.



## Build a model
Lets build a model for each country, lifeExp ~  year


```{r}

# Fit models --------------------------------------------------------------

country_model <- function(df){
  lm(lifeExp  ~  year1950, data=df)  # use year1950 because the absolute value is not important
}
models <- by_country %>%
  mutate(
    model = map(data, country_model)
  )
models
lm(lifeExp  ~  year1950, data=by_country$data[[1]]) 
models$model[1]

```

### Combine data wrangling and model building

```{r}

# Put it all together -----------------------------------------------------

by_country <- gapminder  %>%
  group_by(continent, country) %>%
  nest() %>%  
  mutate(
    model = map(data, country_model)
  )

by_country
```



## Get the model data in a tidy form using the **broom** package

```{r}
models <- models %>%
  mutate(
    glance  = map(model, broom::glance),        # Construct a single row summary "glance" of a model
    rsq     = glance %>% map_dbl("r.squared"),  # note the pipe within mutate(...)
    tidy    = map(model, broom::tidy),          # Tidy the result of a test into a summary data.frame
    augment = map(model, broom::augment)        # add columns to the original dataset such as predictions, residuals and cluster assignments
  ) 
models
models$glance[1]
models$rsq[1]
models$tidy[1]
models$augment[1]
```

### Investigate how well the model fits 


```{r}

models %>% 
  ggplot(aes(rsq, country)) +
  geom_point(aes(colour = continent)) 
# source("gapminderShiny.R")
```

is the plot clear? how could it be improved?



ggplot orders categorical variables alphabetically 

```{r}

models %>% 
  ggplot(aes(rsq, reorder(country, rsq))) +
  geom_point(aes(colour = continent)) 

```

### Find the countries with the worst fit


```{r}

  models %>% filter((rsq<0.1 & rsq>0))  %>% unnest(rsq)  %>% top_n(6,rsq) %>% unnest(data) %>% 
    ggplot(aes(year, lifeExp)) +
    geom_line(aes( alpha = 1/3))  +
    facet_wrap(~country)
  
```

# How much did the countries improve life expectancy over time


```{r, message=FALSE, warning=FALSE}
library(plotly)
# Unnest data -------------------------------------------------------------

unnest(models, data)
unnest(models, glance, .drop = TRUE) 
unnest(models, tidy)

# Plot data frame ---------------------------------------------------------


plotLife <- models %>%
  unnest(tidy) %>%
  select(continent, country, term, estimate, rsq) %>%
  spread(term, estimate) %>%
  ggplot(aes(`(Intercept)`,year1950))+
  geom_point(aes(colour = continent, size = rsq, fill = country)) +
  geom_smooth(se=FALSE) +
  xlab("Life expectancy (1950)") +
  ylab("Yearly improvement") +
  scale_size_area() + guides(fill=FALSE)
ggplotly(plotLife, tooltip = c("year1950", "country"))



```
## where are the exeptions

```{r}

unnest(models, augment) # using the unnest with one augment argument keeps the grouping variables and augment 

models %>% unnest(augment) %>% 
  ggplot(aes(year1950, .resid)) +
  geom_line(aes(group = country), alpha = 1/3) +
  geom_smooth(se = FALSE) +
  geom_hline(yintercept = 0, colour = "white") +
  facet_wrap(~continent, scales = "free_y") 


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).