---
title: "Read Json"
output:
  html_notebook: default
  html_document: default
---

# Read in json files

Andreas würde gerne folgende json daten einlese
Luftdaten Info
Feinstaubsensoren OK Lab
http://api.luftdaten.info/static/v1/data.json

according to hadley use jsonlite to read in json data

```{r}
library(jsonlite)
library(tidyverse)
library(rvest)

```

use rvest from hadley to web scrap data

```{r}
library(rvest)
Sensorenwerte <- read_html("http://api.luftdaten.info/static/v1/data.json")
class(Sensorenwerte)

```
hmm, got an xml doc, not  what i was looking for...

according to hadley use jsonlite to read in json data from file or the web

```{r}
Sensorenwerte <- fromJSON("http://api.luftdaten.info/static/v1/data.json", simplifyDataFrame = TRUE, flatten = TRUE)
class(Sensorenwerte)
```

got a data.frame, that is promissing   
lets see what is inside

```{r}
names(Sensorenwerte)
str(Sensorenwerte)
```

the file is somewhat nested, so unnest it

```{r unnest_sensor_data}
Sensorenwerte %>% unnest(.sep = "_") -> Sensorwerte_unnest
Sensorwerte_unnest %>% select(timestamp)
str(Sensorwerte_unnest)
```

set date format for time stamp

```{r}
library(lubridate)
Sensorwerte_unnest %>% mutate(timestamp = as.Date(timestamp)) -> Sensorwerte_unnest
str(Sensorwerte_unnest)
```

- sensordatavalues_value
- location.longitude
- location.latitude

have charater class instead of numeric

```{r}
Sensorwerte_unnest %>% mutate(sensordatavalues_value = as.numeric(sensordatavalues_value), location.longitude = as.numeric(location.longitude), location.latitude = as.numeric(location.latitude) ) -> Sensorwerte_numeric
  str(Sensorwerte_numeric)
```


now we have the right data format, lets do some plots

```{r}
Sensorwerte_numeric %>% ggplot + geom_point(aes(timestamp, sensordatavalues_value, color = sensor.sensor_type.id))
```


create list of sensor ids and how often they occur 

```{r}
Sensorwerte_numeric %>% count(sensor.id) %>% arrange(desc(n))
```

```{r}
Sensorwerte_numeric %>% count(location.id)  %>% arrange(desc(n))
```


seems like there are more sensors on a given loction

```{r}
Sensorwerte_numeric %>% group_by(location.id, sensor.id) %>% summarise(n = n())-> Sensor_grouped
```


lets create a map with the sensors location  
leaflet did not work in the beginning, adding "  html_document: default" in yaml header helped

map shows in editor and preview but at times not in browser  

install devtools::install_github("rstudio/leaflet")

```{r}

Sensorwerte_numeric %>% distinct(location.longitude,location.latitude) -> Sensors_distinct_location

library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=Sensors_distinct_location$location.longitude, lat= Sensors_distinct_location$location.latitude, popup="Feinstaubsensor")
m  # Print the map
```



ggmap seems the solution but get an error 
Error: GeomRasterAnn was built with an incompatible version of ggproto. Please reinstall the package that provides this extension.
Console~/CloudProjectsUnderWork/ProjectsUnderWork/VhsDataVisualization/Rkenntnisse_2_2017/
			

then install devtools::install_github("dkahle/ggmap") based on http://stackoverflow.com/questions/40642850/ggmap-error-geomrasterann-was-built-with-an-incompatible-version-of-ggproto

solved the issue but then leaflet worked and is interactive and nicer...
```{r}
library(ggmap)

map <- get_map(location = 'Germany', zoom = 7)
ggmap(map) 
```






